---
title: "hp2"
author: "Frederick Kusumo"
date: 2023-04-18
format: 
  html:
    embed-resources: true
editor: visual
editor_options: 
  chunk_output_type: console
---
# Introduction

A national anthem is generally a way of highlighting the history, tradition, and culture of the country in the form of word and song. When you think about it, they would always be empowering as they are trying to honor and show how the country has come to its form to this date. However, it would be really interesting to find out a lot of things regarding the national anthems of different countries through applying the skills that have been learned in class particularly regarding strings, and sentimental analysis.

The data set I am using for this project is from Kaggle which contains 5 different columns; Country, Alpha.2, Alpha.3, Continent, and Anthem. In this project, I am going to use just the Country, Continent, and Anthem. The Country column tells which country the anthem is from, the Continent column tells us regarding the region of where the country is located, and the Anthem column contains anthems from different countries translated to English.

What I am specifically looking at for in this project would specifically be regarding the sentiment and words of the different Anthems. My first question would be regarding the top 5 most words used in anthems across different Continent. My second question would be specifically just focusing on positive and negative words generally. The third question would be regarding the most popular phrases across the different Continents, and last question would be regarding highest and lowest 5 sentimental score of the anthems per country. These questions would enable to answer my curiosity regarding anthems. Anthems should generally be positive and empowering. But, after doing this project, I will know if that is true or not. 

A disclaimer would be that this analysis would be a little bit inaccurate due to national anthems as a whole would be in different languages respective to their country, since this data contains anthems were translated to English, some of the lines or phrases could have lost their original meaning.

# Setup

```{r}
here::i_am("hp2-frederickkusumo/index.qmd")
library(here)
library(tidyverse)
library(tidytext)
```

```{r}
national_anthems <- read.csv('national_anthems.csv')
national_anthems <- national_anthems %>% 
  select(-c(Alpha.2, Alpha.3))
```

Here I am omitting unnecessary columns like Alpha.2 and Alpha.3 to make the data frame more neat and clear.

#1. What are the top words used in national anthems across the different Continents?

```{r}
anthems_freq <- anthems_tidy %>% 
  group_by(Continent) %>% 
  count(word, sort=TRUE)

anthems_freq <- anthems_freq %>% 
  group_by(Continent) %>% 
  slice(1:5)
```

```{r}
anthems_freq %>% 
  ggplot() +
  aes(x = n,
      y = reorder(word, n),
      fill = n) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~Continent, scales = "free") +
  labs(title = 'Top 5 Most Popular Words in National Anthems per Continent',
       x = 'Word Frequency',
       y = 'Words') 
```


#2. What are the top 10 positive and negative words widely used in national anthems generally?

```{r}
anthems_tidy <- national_anthems %>% 
  unnest_tokens(word, Anthem) %>% 
  anti_join(stop_words)

anthems_sentiment <- anthems_tidy %>% 
  inner_join(get_sentiments("bing")) %>% 
  count(word, sentiment, sort = TRUE) %>% 
  ungroup()
```

```{r}
anthems_sentiment %>% 
  group_by(sentiment) %>% 
  slice_max(n, n = 10) %>% 
  ungroup() %>% 
  mutate(word = reorder(word, n)) %>% 
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(title = "Anthems Top 10 Positive and Negative Words",
       x = "Word Count")
```

# 3. What would be the most popular phrases used in the national anthems per Continent?
 
```{r}
anthems_phrases <- national_anthems %>% 
  unnest_tokens(phrase, Anthem, token = "ngrams", n = 3)
```
 
```{r}
anthems_phrases <- anthems_phrases %>% 
  separate(col = phrase,
           into = c("word1", "word2", "word3"),
           sep = " ",
           remove = FALSE) 
```

```{r}
anthems_phrases_stop <- anthems_phrases %>% 
  filter(!word1 %in% stop_words$word & !word2 %in% stop_words$word & !word3 %in% stop_words$word)

anthems_phrases_top <- anthems_phrases_stop %>% 
  group_by(Continent) %>% 
  count(phrase, sort = TRUE)

anthems_phrases_top <- anthems_phrases_top %>% 
  group_by(Continent) %>%
  arrange(desc(n)) %>%
  filter(row_number() == 1)
```

```{r}
anthems_phrases_top %>% 
  ggplot(aes(x = reorder(phrase, n),
             y = n, 
             fill = Continent)) +
  geom_col() +
  labs(
    x = NULL, 
    y = 'frequency',
    title = "Most frequent phrases in National Anthems per Continent") +
  coord_flip() +
  theme_minimal()
```

# 4. Which counttries generally have the top and lowest sentiment score based on their national anthems?

```{r}
sentiment_country <- anthems_tidy %>% 
  inner_join(get_sentiments("bing")) %>% 
  count(Country, index = row_number() %/% 50, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative) %>% 
  arrange(desc(sentiment))
```

```{r}
top_sentiment <- sentiment_country %>% 
  slice(1:5)

low_sentiment <- sentiment_country %>% 
  slice(236:241)

top_low_sentiment <- bind_rows(top_sentiment, low_sentiment)
```

```{r}
top_low_sentiment %>% 
ggplot(aes(x = reorder(Country, sentiment), 
           y = sentiment,
           fill = Country)) +
  geom_col() + 
  theme(axis.text.x = element_text(angle = 45, size = 5)) + 
  labs(
    x = 'Countries',
    title = "Top 5 Lowest and Highest Sentiment"
  )
```

